\begin{recipe}{Curried Bean Burgers}{Eric King}

\begin{RecipeDescription}
Pan-fried bean-and-vegetable patties seasoned with curry spices.
Moisture control is the whole game; dry the mix a bit, and they hold together beautifully.

\EstimatedNutrition{}{}{}{}{}
\end{RecipeDescription}

\bigskip

\begin{recipecols}

\begin{Ingredients}
\item 2 cans beans (black, red, pinto, etc.)
\item 3 carrots
\item 2 medium sweet potatoes
\item 1 egg
\item Canola oil, for frying
\item Rajma curry spice mix or warm curry spice mix
\end{Ingredients}

\RecipeColumnBreak

\begin{Procedure}
\item Shred the carrots.
Drain off excess moisture.
Alternatively, spread on a plate and microwave for 90 seconds.
Fluff with a fork, then let additional moisture evaporate.
\item Microwave the sweet potatoes for about 5 minutes each.
Scoop out the insides and set aside.
\item Drain the beans.
Optionally microwave them on a plate for 2 minutes, then let them steam off to remove excess moisture.
\item Once cooled, combine beans, carrots, sweet potato, egg, and spices in a bowl.
Hand-mash until it holds together.
A food processor can work better; consider reserving a small amount of hand-mashed beans to add back for texture.
The more intact bean pieces you keep, the harder it is to get patties to bind.
\item Form about 8 patties.
Roll into balls, then flatten into patties.
\item Fry in a small amount of canola oil, just enough to form a light crust on each side.
\end{Procedure}

\end{recipecols}

\begin{Notes}
If the mixture feels wet, let it rest 5--10 minutes before forming patties.
If the patties won’t hold together, mash (or briefly process) a bit more to increase binding.
\end{Notes}

\end{recipe}
