% recipes/basic_bread.tex
\begin{recipe}{Eric's Basic Bread}{Eric King}

\begin{RecipeDescription}[images/fresh-white-bread-close-up][0.4\textwidth][Public Domain Image]
A simple, reliable loaf with stuff that I always have around the kitchen; it comes out great every time.
Was a favorite of mine to make while living in Syracuse with a nice soup on a cold day.
Takes two hours to rest the dough and 45 minutes to bake. 
% \EstimatedNutrition{<servings>}{<cal>}{<protein>}{<carbs>}{<fat>}
\EstimatedNutrition{1 (Loaf)}{1900}{41}{302}{58}
\end{RecipeDescription}

\begin{recipecols}

\begin{Ingredients}
\item 3 cups flour
\item 1 1/4 cups warm water
\item 1/4 cup olive oil
\item 1/2 tsp salt
\item 1 packet yeast
\item 1 Tbsp sugar
\end{Ingredients}

\RecipeColumnBreak

\begin{Procedure}
\item Combine warm water, sugar, and yeast. Allow yeast to activate.
\item Add flour, olive oil, and salt. Mix with a durable spoon until thoroughly combined.
\item Let dough rest 2 hours in a warm location, covered. Dough will roughly double in size.
\item Punch dough down. Either let rise again for another 2 hours (softer, yeastier), or form into a ball. A wetter dough yields a flatter artisan loaf; a drier dough yields a rounder loaf. This is your chance to gently knead in a bit more flour if desired.
\item Place dough ball on a baking sheet. Lightly oil the top to prevent drying. Cover lightly (towel, plastic wrap, or foil) and let rise about 30 minutes.
\item Preheat oven to 425°F. Place a water bath in the oven. Once preheated, uncover dough and place the baking sheet in the oven.
\item Bake 42--45 minutes.
\end{Procedure}

\end{recipecols}

\end{recipe}

